---
title: "Report II "
author: "Yang yang,Wang hao,Jiang heng,Guo siying"
date: "2020/10/25"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(reshape2)
require(ggplot2)
require(ggthemes)
theme_set(theme_minimal())
require(GGally)
require(ggExtra)
require(tinytex)
```

## Implement the densities of the K and G0 distributions for intensity data

Get bright image data from the "ImagematrXI" library for analysis.

```{r LoadUrbanHVData}
source("C:/Users/ASUS/Desktop/SAR-Course-2020-main/Code/R/imagematrix.R")
load("C:/Users/ASUS/Desktop/SAR-Course-2020-main/Code/R/bright.Rdata")
# Inspect what they are in the Environment window
```

Below is information about the data, including its type, dimensions, and scope.

```{r Quantitative_EDA_Urban}
typeof(bright)
dim(bright)
range(bright)

vector.bright <- data.frame(bright=as.vector(bright))
summary(vector.bright)
```

We can analyze the data with boxplot and histogram to Move to graphical representations of the data, the outliers are shown in blue.


```{r Graphical_EDA_Urban_Boxplot, fig.cap='Boxplots with notches', fig.subcap=c('Linear scale', 'Semilogarithmic scale'), out.width = "50%", fig.align = "center"}
ggplot(vector.bright, aes(x=bright)) +
  geom_boxplot(notch = TRUE)+
  geom_boxplot(outlier.colour="blue", outlier.shape=7,outlier.size=1)+
  ggtitle("bright")

ggplot(vector.bright, aes(x=bright)) +
  geom_boxplot(notch = TRUE) +
  geom_boxplot(outlier.colour="blue", outlier.shape=7,outlier.size=1)+
  scale_x_log10()+
  ggtitle("bright in semilog scale")
```

Our first step is to obtain a box plot of bright image data, named "bright". It can be seen that the "bright" graphic frame is very flat. Therefore, we perform a logarithmic transformation on the data and get the graph titled "Brightness on a semi-logarithmic scale" in the figure below.
As shown in the "Brightness on a Semi-Logarithmic Scale" graph below, the average value of the data is around 10^5.
Then we supplemented the information with a histogram of the data, and displayed it with a block diagram and used the Freedman-Diaconis rule to construct the histogram, which included using bins of equal size: $\frac32 \text{IQR}(z) / n^{1/3}$.

```{r Graphical_EDA_Urban_Histogram, fig.cap='Histograms', fig.subcap=c('Linear scale', 'Semilogarithmic scale'), out.width = "50%", fig.align = "center"}
ggplot(vector.bright, aes(x=bright)) +
  geom_histogram(aes(y=..density..),
                 bins=nclass.FD(unlist(vector.bright)),
                 col="blue", fill="white")+
  ggtitle("bright")

ggplot(vector.bright, aes(x=bright)) +
  geom_histogram(aes(y=..density..),
                 bins=nclass.FD(unlist(vector.bright)),
                 col="blue", fill="white") +
  scale_x_log10()+
  ggtitle("bright in semilog scale")
```
We merge the second box plot into the second histogram:

```{r Graphical_EDA_BoxplotAndHistogram}
ggplot(vector.bright, aes(x=bright)) +
  geom_histogram(aes(y=..density..),
                 bins=nclass.FD(unlist(vector.bright)),
                 col="blue", fill="white") +
  geom_boxplot(aes(y=0.8), width=.1,col="yellow", notch=TRUE) +
  ylab("Density and Boxplot") +
  xlab("Intensity in semilogarithmic scale") +
  scale_x_log10()
# Try reducing the number of bins
```
After analysis, we can draw the following two conclusions:
*The data is positive and symmetric
*Data has a large dynamic range
Then, we can pay attention to the "natural" domain of the data: as an image.
The "imagematrix" library requires data in the range of $[0,1]$, and we implement a function to perform this mapping.

```{r}
plot(imagematrix(normalize(bright)))
```

Nothing can be seen in the picture above. The reason is that there are some very large values ​​that "flatten" most observations to very deep grays. And we want a unified histogram.

Since the continuous random variable $Zcolon \ Omega \ to \ mathbb R$ cumulative distribution function $F_Z$, the random variable $W = F_Z (Z)$ has a uniform distribution.

The cumulative distribution function of $W$ can be obtained as $F_W (w) = / Pr (W / leq w) = / Pr (F_Z (Z) / leq w) $.

Since $Z$ is continuous, there is the inverse of its cumulative distribution function $F ^ {-1} _Z$.
Then we can rewrite it as
$F_W (w) = Pr (F_Z (Z) / leq w) = Pr (F ^ {-1} _Z (F_Z (Z)) \ leq F_Z ^ {-1} (w)) = Pr (Z \ leq F ^ {-1} _Z(w))$.
This happens to be the cumulative distribution function of $Z$ at $F^{-1} _Z(w)$, so we can prove $F_W(w) = F_Z(F ^{-1} _Z(w)) = w$, which represents a uniform random variable on $(0,1)$.

One of the easiest ways to estimate the cumulative distribution function based on the data $z = (z_1, \dots, z_n)$ is to use the empirical cumulative distribution function, or just use the "empirical function".
It is only a finite approximation defined by the cumulative distribution function, given by the following formula
\begin{equation}
\ wide-hat {F}(t) = frac1n # # # j # text{ such that} z_j/leq t/} ,
\End of the Dusk {formula}
where $#$ denotes the number of elements in the set.

The original data and its empirical function are shown as following:

```{r OriginalDataEmpiricalFunction}
ggplot(vector.bright, aes(x=bright)) +
  geom_histogram(aes(y=..density..),
                 bins=nclass.FD(unlist(vector.bright))/50,
                 col="black", fill="white") +
  stat_ecdf(col="blue") +
  ylab("Density and Empirical function") +
  xlab("Intensity in semilogarithmic scale") +
  scale_x_log10()
```

Such data can be implemented as:

```{r HistogramEqualization}
# First, we compute the empirical function
ecdf.bright <- ecdf(unlist(vector.bright))

# Then, we apply this function to the data
eq.bright <- ecdf.bright(unlist(vector.bright))

# Finally, we restore the matrix organization of the data
dim(eq.bright) <- dim(bright)

# And we see the result
plot(imagematrix(eq.bright))
```

Now, we perform EDA on the balanced data.

```{r EDA_EqualizedData}
summary(as.vector(eq.bright))

vector.eq.bright <- data.frame(eq.bright=as.vector(eq.bright))
                              
ggplot(vector.eq.bright, aes(x=eq.bright)) +
  geom_histogram(aes(y=..density..),
                 bins=nclass.FD(unlist(vector.eq.bright)),
                 col="black", fill="white") +
  geom_boxplot(aes(y=1.2), width=.1, notch=TRUE) +
  ylab("Density and Boxplot") +
  xlab("Equalized data") 

```

In the figure above, the uniform pixel distribution characteristics of the new image after the transformation are shown.

We can also directly perform logarithmic conversion on the data, and the result is shown in the figure below.

```{r LogarithmImageTransformation}
plot(imagematrix(normalize(log(bright))))
```

When changing the parameters in the histogram, we can see the following results.
An example of performing this effect using a sample of $n = 300$ is as follows.

#Gamma Distribution

```{r BinSizeEffect, fig.cap='Histograms', fig.subcap=c('Default bin size', 'Freedmand-Diaconis bin size', "Improved histogram"), out.width = "50%", fig.align = "center"}
x <- data.frame(x=rgamma(300, shape=2, scale=1))

ggplot(x, aes(x=x)) +
  geom_histogram(aes(y=..density..),
                 col="blue", fill="white") +
  ylab("Proportions histogram")

ggplot(x, aes(x=x)) +
  geom_histogram(aes(y=..density..),
                 bins=nclass.FD(unlist(x)),
                 col="blue", fill="white") +
  ylab("Proportions histogram")

ggplot(x, aes(x=x)) +
  geom_density(col="blue", size=2) +
  geom_histogram(aes(y=..density..),
                 bins=nclass.FD(unlist(x)), 
                 alpha=0.5, fill="#33AADE", color="black") +
  ylab("Histogram and smoothed histogram")

```

Comparing the first picture and the second picture, we can see that the more boxes there are, the more data we can obtain, and the more difficult it is for us to process them.

#K Distribution
```{r OriginalDataEmpiricalFunction1}

#Calculation process
a_K=5
v_K=2
L_K=7
pk_num=1e5
array_K=1e5

r_k<-seq(1e-5,1e2,length.out = array_K) # array
x1 <- dgamma(r_k, shape=1, scale=L_K)
x2 <- dgamma(r_k, shape=a_K/v_K, scale=a_K)
x=x1*x2

vector.x <- data.frame(r_G0=as.vector(r_k),x=as.vector(x))
vector.x1 <- data.frame(r_G0=as.vector(r_k),x=as.vector(x1))
vector.x2 <- data.frame(r_G0=as.vector(r_k),x=as.vector(x2))

ggplot(vector.x, aes(x=r_k, y=x, group=1)) +
  geom_line(linetype="solid",col="blue")+
  ylab("PDF-x(x=x1*x2)")+
  scale_x_log10()
ggplot(vector.x1, aes(x=r_k, y=x1, group=1)) +
  geom_line(linetype="solid",col="blue")+
  ylab("PDF(x1)")+
  scale_x_log10()
ggplot(vector.x2, aes(x=r_k, y=x2, group=1)) +
  geom_line(linetype="solid",col="blue")+
  ylab("PDF(x2)")+
  scale_x_log10()

# K-random
r_k<-runif(pk_num, min = 0, max = 1) # 0-1 random
x1 <- qgamma(r_k, shape=1, scale=L_K)
x2 <- qgamma(r_k, shape=a_K/v_K, scale=a_K)
x=x1*x2
x<-data.frame(x) # x~K(a,v,L)

ggplot(x, aes(x=x)) +
  geom_histogram(aes(y=..density..),alpha=0.5, fill="#6495ED", color="black",bins=nclass.FD(unlist(x))/50) +
  geom_density(col="red", size=1) +
  geom_boxplot(aes(y=1), width=.1, notch=TRUE)+
  stat_ecdf(col="yellow") +
  ylab("Histogram and smoothed histogram")+
  scale_x_log10()

```
#G0 Distribution
```{r BinSizeEffect1, fig.cap='Histograms', fig.subcap=c('Default bin size', 'Freedmand-Diaconis bin size', "Improved histogram"), out.width = "50%", fig.align = "center"}

a_G0=-2
r_G0=5
L_G0=12
pG0_num=1e5
array_G0=1e5

#Calculation process
r_G0<-seq(1e-5,1e2,length.out = array_G0) #  array
x1 <- dgamma(r_G0, shape=1, scale=L_G0)
x2 <- dgamma(r_G0, shape=-a_G0, scale=r_G0)
x=x1/x2
x<-data.frame(x)

vector.x <- data.frame(r_G0=as.vector(r_G0),x=as.vector(x))
vector.x1 <- data.frame(r_G0=as.vector(r_G0),x=as.vector(x1))
vector.x2 <- data.frame(r_G0=as.vector(r_G0),x=as.vector(x2))

ggplot(vector.x, aes(x=r_G0, y=x, group=1)) +
  geom_line(linetype="solid",col="blue")+
  ylab("PDF-z=x/y")+
  scale_x_log10()
ggplot(vector.x1, aes(x=r_G0, y=x1, group=1)) +
  geom_line(linetype="solid",col="blue")+
  ylab("PDF-x`r(1,L)")+
  scale_x_log10()
ggplot(vector.x2, aes(x=r_G0, y=x2, group=1)) +
  geom_line(linetype="solid",col="blue")+
  ylab("PDF-x`r(-a,r)")+
  scale_x_log10()

# G0-random
r_G0<-runif(pG0_num, min = 0, max = 1) # 0-1 random
x1 <- qgamma(r_G0, shape=1, scale=L_G0)
x2 <- qgamma(r_G0, shape=-a_G0, scale=r_G0)
x=x1/x2
x<-data.frame(x) # x~G0(a,r,L)

ggplot(x, aes(x=x)) +
  geom_histogram(aes(y=..density..),alpha=0.5, fill="#6495ED",color="black",bins=nclass.FD(unlist(x))/50) +
  geom_density(col="blue", size=1) +
  ylab("Histogram and smoothed histogram")+
  scale_x_log10()

```
